Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-01-07 Manuscript/manuscript.Rmd
updated manuscript

# Figure 4: Class Imbalance

@@

# Figure 5: Performances of Models with No Class-Balancing

@@

# Figure 6:

@@

A list of various metrics used to assess predictive performances for models that were built on fully imbalanced datasets.

>>>>

## Figure 4: Class Imbalance

@@

## Figure 5: Performances of Models with No Class-Balancing

@@

## Figure 6: Performances of Models with Randomly Under-sampled Data.

Barplots measuring the predictive performance of models built on datasets using 50 iterations of random under-sampling. The performance metrics considered were accuracy, AUC, F1-Score, and MCC. Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).

@@

Results of various metrics used to assess predictive performances for models that were built on fully imbalanced datasets.

## Figure 1: Performances of Models with Both SMOTE-Balanced and Randomly Over-sampled Data.

Barplots measuring the predictive performance of models built on datasets using 50 iterations of both the SMOTE algorithm (A) and random over-sampling (B).  The performance metrics considered were accuracy, AUC, F1-Score, and MCC. Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).

## Table 4:

Results of various metrics used to assess predictive performances for models that were built on random under-sampled datasets.

## Table 5:

Results of various metrics used to assess predictive performances for models that were built on both SMOTE-balanced and random over-sampled datasets.
